### 2019-10-16 thesis/txt/0-introduction.tex
fixes from Taicos introduction review

%With our work we want to support developers, researchers or project managers in deciding which technique is the best one for their use case. 
Continuous Integration (CI) has become a best practice in software engineering and many software projects now use CI~\cite{hilton2016usage,staahl2014modeling,beller2017oops} to detect bugs more easily~\cite{vasilescu2015quality,duvall2007continuous} and improve developer productivity~\cite{miller2008hundred,hilton2016usage} and communication~\cite{downs2012ambient}. A build on a CI server typically not only compiles and packages the software, but also executes test~\cite{beller2017oops} and various kinds of static analysis~\cite{zampetti2017open}.

CI builds often produce very long and verbose build logs~\cite{beller2017oops}, stating the progress and results of the various steps within the build. The structure of these logs changes greatly from project to project and highly depends on the tools and environment used.
Build logs are a highly valuable data source. First of all, for the developers that read them to analyze why their build failed or how different stages of the build process perform.
Second, for researchers that can harvest the information contained in the logs --- and their metadata --- to study the software engineering process of a project.
However these two groups can only utilize the information within the build logs if they can adequately extract the information relevant to them.

There are many different retrieval techniques used for this task. Beller et al. used regular expressions when analyzing the failure reasons of Ruby and Java Maven build logs from TravisCI~\cite{beller2017oops}. Such regular expressions are developed by looking at a few exemplary build logs and maintaining them whenever new cases are introduced is a tedious and error-prone task~\cite{michael2019regexes}.
Vassallo et al. wrote a custom parser for Java Maven build logs to gather information for build repair hints~\cite{vassallo2018un-break}.
Recently Amar et al. greatly reduced the number of build log lines for a developer to inspect by creating a diff between the logs from a failed and successful build~\cite{amar2019mining}.

Currently we only have anecdotal evidence on the performance of these techniques and when to use which. Developers and researches have little support while choosing which one to use for an retrieval task. Our goal for this thesis is to investigate different information retrieval techniques and describe under which circumstances we recommend each of the techniques.

We aim to define a model to characterize the different retrieval techniques and answer what influences the suitability of a technique.
We support our assumption by evaluating three chosen techniques, namely regular expression synthesis by example using the Microsoft PROSE library (referred to as PBE), a common text similarity approach (referred to as TS) and simple keyword search (referred to as SKWS).
Our \emph{Failing Build Logs Data Set} encompasses about 800 log files from 80 repositories, labeled with the log part describing the reason a build failed, keywords to search for this retrievals and a categorization of the retrievals according to their structural position within the log.

We aim to answer the following research questions:
\begin{itemize}
  \item[\textbf{RQ1:}] What criteria influence the suitability of an information retrieval technique for CI build logs?
  \item[\textbf{RQ2:}] When are PBE, TS and SKWS suited to extract information from CI build logs?
  \item[\textbf{RQ2.1:}] How many examples do PBE, TS and SKWS need to perform best?
  \item[\textbf{RQ2.2:}] How accurate are the retrievals of PBE, TS and SKWS?
  \item[\textbf{RQ2.3:}] How structurally similar do the examples for PBE and TS need to be for the techniques to be applicable?
\end{itemize}

\plan{results and conclusions of my work}
Our study of the three techniques on \emph{Failing Build Logs Data Set} shows that PROSE is suitable for retrieval tasks requiring a high precision, ... . Extracting information by using text similarity of examples is suitable when ... . Simple keyword search is suitable ... .

\paragraph{Our work contributes:}
\begin{itemize}
  \item A model of the extractable information in CI build logs
  \item A model to characterize information retrieval techniques from CI build logs
  \item A model to characterize use case scenarios for information retrieval from CI build logs
  \item A tool unifying several information retrieval techniques namely:
        \begin{itemize}
          \item our implementation of regular expression program synthesis using the Microsoft PROSE library (PBE),
          \item a common information retrieval approach using text similarity (TS), and
          \item a simple keyword search approach (SKWS)
        \end{itemize}
  \item The \emph{LogCollector}, a tool to gather build logs from Travis CI
  \item A validated data set of about 800 logs from failed Travis CI builds labeled with:
        \begin{itemize}
          \item the substring of the log describing the reason the build failed,
          \item keywords developers would use to search for these descriptions of the build failure reason, and
          \item a categorization of the retrievals according to their structural position within the build log
        \end{itemize}
  \item An evaluation of our model for the three implemented information retrieval techniques \todo{describe \emph{what} we look for with this evaluation}
  \item A extendable scheme supporting decision on (our three) information retrieval techniques relative to a given use case scenario
\end{itemize}

This thesis first presents an overview over the related research, spanning from CI research, build log analysis and augmentation, and common \todo{production?} log processing over information retrieval techniques to program synthesis by examples.
Next, chapter \ref{sec:models} present our models for information retrieval techniques, use case scenarios for such techniques and extractable information from CI build logs. It also introduces the three techniques, we focus on during our research evaluation, as well as their theoretical foundations.
Chapter \ref{sec:data-set} describes the creation of our \emph{The Failing Build Logs Data Set} collected from failed Travis CI build logs, and the labeling and validation process.
Following, Chapter \ref{sec:implementation} our implementation of the three chosen information retrieval techniques and the usage of our unified information retrieval tool.
This tool is also used for the evaluation study of our models described in Chapter \ref{sec:study}. There we also describe the resulting instantiation of our recommendation model for regex program synthesis, text similarity and keyword search.
Lastly, we conclude and give an overview of further research opportunities in Chapter \ref{sec:conclusion}.
\end{document}

>>>>

%With our work we want to support developers, researchers or project managers in deciding which technique is the best one for their use case. 
Continuous Integration (CI) has become a best practice in software engineering.
Many software projects now use CI~\cite{hilton2016usage,staahl2014modeling,beller2017oops} to detect bugs more easily~\cite{vasilescu2015quality,duvall2007continuous} and improve developer productivity~\cite{miller2008hundred,hilton2016usage} and communication~\cite{downs2012ambient}.
A build on a CI server typically not only compiles and packages the software, but also executes tests~\cite{beller2017oops} and various kinds of static analyses~\cite{zampetti2017open}.

CI builds produce long and verbose build logs~\cite{beller2017oops}, stating the progress and results of the various steps within the build. The structure of these logs changes greatly from project to project~\cite{staahl2014modeling} as it highly depends on the tools and environment used.
Build logs are a valuable data source. First of all, for developers, who read them to analyze why their build failed or how different stages of the build process perform.
Second, they are valuable for researchers, who can harvest the information contained in the logs --- and their metadata --- to study the software engineering process of a project.
However, these two groups can only utilize the information within the build logs if they can adequately retrieve the information relevant to them.

There are different retrieval techniques used to retrieve information from CI build logs. Beller et al. use regular expressions to analyze the failure reasons of Ruby and Java Maven build logs from TravisCI~\cite{beller2017oops}.
In general, such regular expressions are developed by looking at a few exemplary build logs and updating them whenever new cases are introduced is a tedious and error-prone task~\cite{michael2019regexes}.
Vassallo et al. wrote a custom parser for Java Maven build logs to gather information for build repair hints~\cite{vassallo2018un-break}.
Recently, Amar et al. greatly reduced the number of build log lines for a developer to inspect by creating a diff between the logs from a failed and successful build~\cite{amar2019mining}.

Currently there is only anecdotal evidence on the performance of these techniques and when a technique should be preferred. Developers and researches have little support while choosing which technique to use for an retrieval task. The goal for this thesis is to investigate different information retrieval techniques and describe under which circumstances we recommend each of the techniques.

We aim to define a model to characterize the different retrieval techniques and answer what influences the suitability of a technique.
We support our assumption by implementing and evaluating three techniques:
\begin{itemize}
  \item regular expression synthesis by example using the Microsoft PROSE library (referred to as PBE),
  \item a common text similarity approach (referred to as TS) and
  \item simple keyword search (referred to as SKWS)
\end{itemize}
To evaluate these techniques we create the \emph{Failing Build Logs Data Set}, which encompasses about 800 log files from 80 repositories. Each log is labeled with the log part describing the reason a build failed, keywords to search for this log part and a categorization of the labeled log part according to its structural position within the log.

We aim to answer the following research questions:
\begin{itemize}
  \item[\textbf{RQ1:}] Which criteria influence the suitability of an information retrieval technique for CI build logs?
  \item[\textbf{RQ2:}] When are PBE, TS and SKWS suited to retrieve information from CI build logs?
  \item[\textbf{RQ2.1:}] How many examples do PBE, TS and SKWS need to perform best?
  \item[\textbf{RQ2.2:}] How accurate are the retrievals of PBE, TS and SKWS?
  \item[\textbf{RQ2.3:}] How structurally similar do the examples for PBE and TS need to be for the techniques to be applicable?
\end{itemize}

\plan{results and conclusions of my work}
Our study of the three techniques on \emph{Failing Build Logs Data Set} shows that PROSE is suitable for retrieval tasks requiring a high precision, ... . Retrieving information by using text similarity of examples is suitable when ... . Simple keyword search is suitable ... .

\paragraph{Our work contributes:}
\begin{itemize}
  \item A model of the retrievable information in CI build logs
  \item A model to characterize information retrieval techniques from CI build logs
  \item A model to characterize use case scenarios for information retrieval from CI build logs
  \item A tool unifying several information retrieval techniques namely:
        \begin{itemize}
          \item our implementation of regular expression program synthesis using the Microsoft PROSE library (PBE),
          \item a common information retrieval approach using text similarity (TS), and
          \item a simple keyword search approach (SKWS)
        \end{itemize}
  \item The \emph{LogCollector}, a tool to gather build logs from Travis CI
  \item A validated data set of about 800 logs from failed Travis CI builds labeled with:
        \begin{itemize}
          \item the substring of the log describing the reason the build failed,
          \item keywords developers would use to search for these descriptions of the build failure reason, and
          \item a categorization of the retrievals according to their structural position within the build log
        \end{itemize}
  \item An evaluation of our model for the three implemented information retrieval techniques \todo{describe \emph{what} we look for with this evaluation}
  \item A extendable scheme supporting decision on (our three) information retrieval techniques relative to a given use case scenario
\end{itemize}

This thesis first presents an overview over the related research, spanning from CI research, build log analysis and augmentation, and common \todo{production?} log processing over information retrieval techniques to program synthesis by examples.
Next, chapter \ref{sec:models} present our models for information retrieval techniques, use case scenarios for such techniques and retrievable information from CI build logs. It also introduces the three techniques, we focus on during our research evaluation.
Chapter \ref{sec:data-set} describes the creation of our \emph{Failing Build Logs Data Set} collected from failed Travis CI build logs and the labeling as well as the validation process.
Following, Chapter \ref{sec:implementation} our implementation of the three chosen information retrieval techniques and the usage of our unified information retrieval tool.
This tool is also used for the evaluation study of our models described in Chapter \ref{sec:study}. There we also describe the resulting instantiation of our recommendation model for regex program synthesis, text similarity and keyword search.
Lastly, we conclude and give an overview of further research opportunities in Chapter \ref{sec:conclusion}.
\end{document}

### 2019-10-16 thesis/txt/2-models.tex
fixes from Taicos introduction review

\chapter{Information Extraction Techniques}
\label{sec:models}
%\includegraphics[page=1, width=\textwidth, trim={0.5cm 0.5cm 0.5cm 0.5cm}, clip]{img/RetreatSeptemberSlides.pdf}
Many different information extraction techniques ... this section describes the conceptional / theoretical results of our thesis ...
We create a model to characterize BLIE techniques so we can discuss their similarities and differences more clearly.
Additionally we present a complimentary model for IE tasks, to describe use cases for BLIE techniques in a structured way.
From our analysis of build logs we share our notion of the extractable information within a build log.

@@

\plan{a build consists of various steps, executed by different tools, these are often orchestrated by at least one overarching tool. // picture: overarching tool travis and it calls different tools which tehn output sequentiall, travis sometimes outputs something in between -> that is how the build log is made up // we have this structure though it is not always apparent from the build log / edges between the systems can look very different, mostly no agreed model, we: look at differen techniques to extract certain pieces of information \emph{without complete parsing the whole log in to a structure} -> we don't necesarrily want to understand the whole log sturcture just extract one specifi information relevant to us}

\section{Extractable Information in Build Logs}
\begin{figure}[h]
  \centering
\includegraphics[page=2, width=\textwidth, trim={0.5cm 0.5cm 0.5cm 0.5cm}, clip]{img/flow-of-research.pdf}
  \caption{Information extractable from build logs}
  \label{fig:build-log-information-draft}
\end{figure}
Continuous integration build logs contain a huge amount of information about the various stages in the CI build they correspond to. In this section we present our model to more precisely describe our notion of a information extractable from a CI build log.

@@

\begin{figure}[h]
	\centering
	\includegraphics[width=\textwidth]{img/mt-graphics-BuildLogInformation.pdf}
	\caption{Build Log Information}
	\label{fig:build-log-information}
\end{figure}
During our inital exploration \& data collection for the \emph{Failing Build Log Data Set}, wanted to get an impression about the information one would want to extract from a build log. Within the Travis CI build logs we found various different informations possibly interesting to be extracted
\begin{itemize}
	\item \textbf{Travis Build Step} A Travis CI build consists of several build steps defined within the Travis CI configuration language. Within the build log each of these steps are framed by \lstinline{travis_fold:start:<build step name>} and \lstinline{travis_fold:end:<build step name>}.
	      A build step contains
	      \begin{itemize}
		      \item \textbf{Build Step Name} The string Travis uses to identify the step within start \& end statements.
		      \item \textbf{Build Step Output} The output generated during the build step. The textual representation of the \texttt{Build Step Output} is the substring between the start \& end statements.
	      \end{itemize}
	\item \textbf{Travis Timing} Travis can measure the time of specified sections of the build process. It represents those by \lstinline{travis_time:start:<timing section id>} and \lstinline{travis_time:end:<timing section id>:start=<start time>,finish=<finish time>,duration=<duration>}
\end{itemize}

@@

\section{Characteristics of Information Extraction Techniques}
\begin{figure}[h]
	\centering
	\includegraphics[page=3, width=\textwidth, trim={0.5cm 0.5cm 0.5cm 0.5cm}, clip]{img/flow-of-research.pdf}
	\caption{Model for an information extraction technique}
	\label{fig:model-ie-technique}
\end{figure}
For this thesis we want to evaluate different Information Extraction Techniques in their application to CI build logs. We focus on techniques that do not attempt or require to parse the structure of a whole build log, but rather focus on extracting just one specific information
A build log information extraction technique (BLIE technique) consumes a build log (text file) and produces a certain output (text). \todo{make picture, output can be contained in log or not, can be continuous substring or selected lines etc.}.
\begin{itemize}
	\item \textbf{Target}{Extractable Information} each extraction technique \todo{instantiation!} targets a specific information
	\item \textbf{Setup Overhead}{Time}
	\item \textbf{Performance}{Performance} split into learning performance
	\item \textbf{Configuration Scope} for one repository/project, a language/logkind, global
\end{itemize}

@@

\section{Information Extraction Tasks}
\begin{figure}[h]
	\centering
	\includegraphics[page=4, width=\textwidth, trim={0.5cm 0.5cm 0.5cm 0.5cm}, clip]{img/flow-of-research.pdf}
	\caption{Model for information extraction task}
	\label{fig:modelt-ie-task}
\end{figure}
aims to describe an information extraction task of a developer or a researcher.
\begin{itemize}
	\item \todo{describe all classes}
	\item{Setup Overhead}{Time}
	\item{Performance}{Performance} split into learning performance
\end{itemize}
\todo{give 2-3 concrete example instantiations here}

\section{PROSE Program Synthesis}
\begin{figure}[h]
  \centering
\includegraphics[page=2, width=\textwidth, trim={0.5cm 0.5cm 0.5cm 0.5cm}, clip]{img/RetreatSeptemberSlides.pdf}
  \caption{Synthesizing regular expression programs by example using PROSE}
  \label{fig:prose-explanation}
\end{figure}
\subsection{Overview}
\emph{Programming by Example (PBE)} is a technique where programs are synthesized according to in and output examples provided by the user. It enables users to create programs without requiring programming knowledge~\cite{mayer2015user}. Applied A to the task of text extraction through regular expressions it relieves the developer from having to understand the whole document structure to solve a single extraction task~\cite{le2014flashextract:}.
We chose to investigate the applicability of generating regular expression programs by example to extracting information from build logs. In this work we refer to our interpretation of this technique as \emph{PBE}. \todo{distinguish PBE for buildlogs}

@@

For our work we chose to look at the applicability of PBE from the \emph{technical} perspective.
We investigate whether current program synthesis techniques are able to learn programs for information extraction tasks in the domain of CI build logs.
Furthermore we gather insights in how PBE has to be applied to yield useable results and perform best.
Our implementation of PBE \todo{which we name technique name x}, is mainly based on the Flash Extract DSL~\cite{flahsextractpaper} of the PROSE library by Microsoft\mention{cite prose website}.
Due to that our technique of text extraction through regular expression programs synthesized is highly influenced by the capabilities of Flash Extract.
In the following we will explain the concept of how we apply PBE to information extraction from CI build logs, the concrete implementation is described in \ref{sec:impl-pbe}.

@@

\todo{explanation of process, the way our tool does it, instantiate model of extraction technique, probably no additional theoretical stuff really needed here?, describe regex programs}

\section{Text Similarity}
\begin{figure}[h]
  \centering
\includegraphics[page=3, width=\textwidth, trim={0.5cm 0.5cm 0.5cm 0.5cm}, clip]{img/RetreatSeptemberSlides.pdf}
  \caption{Extracting information using text similarity}
  \label{fig:text-similarity-explanation}
\end{figure}
\paragraph{Overview}
Information retrieval techniques are more and more prevalently used to extract textual information from unstructured textual sources~\mention{stuff annibale is referencing?}. We describe CI build logs as semi-structured, 
\todo{explanation of process, the way our tool does it, instantiate model of extraction technique, probably no additional theoretical stuff really needed here?}

\section{Keyword search}
\begin{figure}[h]
  \centering
\includegraphics[page=4, width=\textwidth, trim={0.5cm 0.5cm 0.5cm 0.5cm}, clip]{img/RetreatSeptemberSlides.pdf}
  \caption{Extracting information using keyword search}
  \label{fig:keword-search-explanation}
\end{figure}
\todo{explanation of process, the way our tool does it, instantiate model of extraction technique, probably no additional theoretical stuff really needed here?}

>>>>

\chapter{Information Retrieval Techniques}
\label{sec:models}
%\includegraphics[page=1, width=\textwidth, trim={0.5cm 0.5cm 0.5cm 0.5cm}, clip]{img/RetreatSeptemberSlides.pdf}
Many different information retrieval techniques ... this section describes the conceptional / theoretical results of our thesis ...
We create a model to characterize BLIE techniques so we can discuss their similarities and differences more clearly.
Additionally we present a complimentary model for IE tasks, to describe use cases for BLIE techniques in a structured way.
From our analysis of build logs we share our notion of the retrievable information within a build log.

@@

\plan{a build consists of various steps, executed by different tools, these are often orchestrated by at least one overarching tool. // picture: overarching tool travis and it calls different tools which tehn output sequentiall, travis sometimes outputs something in between -> that is how the build log is made up // we have this structure though it is not always apparent from the build log / edges between the systems can look very different, mostly no agreed model, we: look at differen techniques to retrieve certain pieces of information \emph{without complete parsing the whole log in to a structure} -> we don't necesarrily want to understand the whole log sturcture just retrieve one specifi information relevant to us}

\section{Retrievable Information in Build Logs}
\begin{figure}[h]
  \centering
\includegraphics[page=2, width=\textwidth, trim={0.5cm 0.5cm 0.5cm 0.5cm}, clip]{img/flow-of-research.pdf}
  \caption{Information retrievable from build logs}
  \label{fig:build-log-information-draft}
\end{figure}
Continuous integration build logs contain a huge amount of information about the various stages in the CI build they correspond to. In this section we present our model to more precisely describe our notion of a information retrievable from a CI build log.

@@

\begin{figure}[h]
	\centering
	\includegraphics[width=\textwidth]{img/mt-graphics-BuildLogInformation.pdf}
	\caption{Build Log Information}
	\label{fig:build-log-information}
\end{figure}
During our inital exploration \& data collection for the \emph{Failing Build Log Data Set}, wanted to get an impression about the information one would want to retrieve from a build log. Within the Travis CI build logs we found various different informations possibly interesting to be retrieved
\begin{itemize}
	\item \textbf{Travis Build Step} A Travis CI build consists of several build steps defined within the Travis CI configuration language. Within the build log each of these steps are framed by \lstinline{travis_fold:start:<build step name>} and \lstinline{travis_fold:end:<build step name>}.
	      A build step contains
	      \begin{itemize}
		      \item \textbf{Build Step Name} The string Travis uses to identify the step within start \& end statements.
		      \item \textbf{Build Step Output} The output generated during the build step. The textual representation of the \texttt{Build Step Output} is the substring between the start \& end statements.
	      \end{itemize}
	\item \textbf{Travis Timing} Travis can measure the time of specified sections of the build process. It represents those by \lstinline{travis_time:start:<timing section id>} and \lstinline{travis_time:end:<timing section id>:start=<start time>,finish=<finish time>,duration=<duration>}
\end{itemize}

@@

\section{Characteristics of Information Retrieval Techniques}
\begin{figure}[h]
	\centering
	\includegraphics[page=3, width=\textwidth, trim={0.5cm 0.5cm 0.5cm 0.5cm}, clip]{img/flow-of-research.pdf}
	\caption{Model for an information retrieval technique}
	\label{fig:model-ie-technique}
\end{figure}
For this thesis we want to evaluate different information retrieval techniques in their application to CI build logs. We focus on techniques that do not attempt or require to parse the structure of a whole build log, but rather focus on extracting just one specific information
A build log information retrieval technique (BLIR technique) consumes a build log (text file) and produces a certain output (text). \todo{make picture, output can be contained in log or not, can be continuous substring or selected lines etc.}.
\begin{itemize}
	\item \textbf{Target}{Extractable Information} each retrieval technique \todo{instantiation!} targets a specific information
	\item \textbf{Setup Overhead}{Time}
	\item \textbf{Performance}{Performance} split into learning performance
	\item \textbf{Configuration Scope} for one repository/project, a language/logkind, global
\end{itemize}

@@

\section{Information Retrieval Tasks}
\begin{figure}[h]
	\centering
	\includegraphics[page=4, width=\textwidth, trim={0.5cm 0.5cm 0.5cm 0.5cm}, clip]{img/flow-of-research.pdf}
	\caption{Model for information extraction task}
	\label{fig:modelt-ie-task}
\end{figure}
aims to describe an information retrieval task of a developer or a researcher.
\begin{itemize}
	\item \todo{describe all classes}
	\item{Setup Overhead}{Time}
	\item{Performance}{Performance} split into learning performance
\end{itemize}
\todo{give 2-3 concrete example instantiations here}

\section{PROSE Program Synthesis}
\begin{figure}[h]
  \centering
\includegraphics[page=2, width=\textwidth, trim={0.5cm 0.5cm 0.5cm 0.5cm}, clip]{img/RetreatSeptemberSlides.pdf}
  \caption{Synthesizing regular expression programs by example using PROSE}
  \label{fig:prose-explanation}
\end{figure}
\subsection*{Overview}
\emph{Programming by Example (PBE)} is a technique where programs are synthesized according to in and output examples provided by the user. It enables users to create programs without requiring programming knowledge~\cite{mayer2015user}. Applied A to the task of text extraction through regular expressions it relieves the developer from having to understand the whole document structure to solve a single extraction task~\cite{le2014flashextract:}.
We chose to investigate the applicability of generating regular expression programs by example to extracting information from build logs. In this work we refer to our interpretation of this technique as \emph{PBE}. \todo{distinguish PBE for buildlogs}

@@

For our work we chose to look at the applicability of PBE from the \emph{technical} perspective.
We investigate whether current program synthesis techniques are able to learn programs for information retrieval tasks in the domain of CI build logs.
Furthermore we gather insights in how PBE has to be applied to yield useable results and perform best.
Our implementation of PBE \todo{which we name technique name x}, is mainly based on the Flash Extract DSL~\cite{flahsextractpaper} of the PROSE library by Microsoft\mention{cite prose website}.
Due to that our technique of text extraction through regular expression programs synthesized is highly influenced by the capabilities of Flash Extract.
In the following we will explain the concept of how we apply PBE to information retrieval from CI build logs, the concrete implementation is described in \ref{sec:impl-pbe}.

@@

\todo{explanation of process, the way our tool does it, instantiate model of retrieval technique, probably no additional theoretical stuff really needed here?, describe regex programs}

\section{Text Similarity}
\begin{figure}[h]
  \centering
\includegraphics[page=3, width=\textwidth, trim={0.5cm 0.5cm 0.5cm 0.5cm}, clip]{img/RetreatSeptemberSlides.pdf}
  \caption{Extracting information using text similarity}
  \label{fig:text-similarity-explanation}
\end{figure}
\paragraph{Overview}
Information retrieval techniques are more and more prevalently used to extract textual information from unstructured textual sources~\mention{stuff annibale is referencing?}. We describe CI build logs as semi-structured, 
\todo{explanation of process, the way our tool does it, instantiate model of retrieval technique, probably no additional theoretical stuff really needed here?}

\section{Keyword Search}
\begin{figure}[h]
  \centering
\includegraphics[page=4, width=\textwidth, trim={0.5cm 0.5cm 0.5cm 0.5cm}, clip]{img/RetreatSeptemberSlides.pdf}
  \caption{Extracting information using keyword search}
  \label{fig:keword-search-explanation}
\end{figure}
\todo{explanation of process, the way our tool does it, instantiate model of retrieval technique, probably no additional theoretical stuff really needed here?}
